---
title: "04_AppliedExercises"
author: "Vasant Marur"
date: "4/3/2021"
output: 
  html_document:
    toc: true
    toc_depth: 4
    toc_float:
      collapsed: false
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#load libraries and data
library(tidyverse)
library(reactable) #interactive tables
library(dygraphs) #interactive time series charting, see http://www.htmlwidgets.org/showcase_dygraphs.html
library(ISLR)
data(Weekly)
Weekly %>% as_tibble(.) ->Weekly_df
```

# Introduction

This is a write up of doing the Applied Exercise of Chap. 4 of ISLR. 
Question 10 Description is below, each part of the question is in subsections below:

> 10. This question should be answered using the Weekly data set, which
> is part of the ISLR package. This data is similar in nature to the
> Smarket data from this chapter’s lab, except that it contains 1, 089
> weekly returns for 21 years, from the beginning of 1990 to the end of 2010.
> 

## Question 10 (a)
> (a) Produce some numerical and graphical summaries of the Weekly
> data. Do there appear to be any patterns?

```{r visualization}
Weekly_df %>%
group_by(Year) %>% mutate(week =row_number()) %>%
ungroup() %>%
select(week,Year,Volume) %>% pivot_wider(., names_from = "Year",values_from = "Volume",names_prefix = "volume_") %>% 
dygraph(main="Volume of shares traded per week",
      ylab = "Billions",xlab = "Weeks",periodicity = "weekly") %>%
dyLegend(show = "onmouseover")

Weekly_df %>%
group_by(Year) %>% mutate(week =row_number()) %>%
ungroup() %>%
select(week,Year,Today) %>% pivot_wider(., names_from = "Year",values_from = "Today",names_prefix = "%return_") %>% 
dygraph(main="Percentage return per week",
      ylab = "Billions",xlab = "Weeks",periodicity = "weekly") %>%
dyLegend(show = "onmouseover")

```

Getting max, min and average ending values for each Year in dataset
```{r num_summaries}
Weekly_df %>% 
  group_by(Year) %>% 
  summarize(min_ending_value = min(Today, na.rm = TRUE),
            max_ending_value = max(Today, na.rm = TRUE),
            Avg_ending_value = round(mean(Today, na.rm = TRUE),digits = 3)) %>% 
  reactable::reactable()

```

## Question 10 (b)
> (b) Use the full data set to perform a logistic regression with
> Direction as the response and the five lag variables plus Volume
> as predictors. Use the summary function to print the results. Do
> any of the predictors appear to be statistically significant? If so,
> which ones?
 

You can also embed plots, for example:

```{r logi-reg-10b, echo=TRUE}
#Weekly_df %>% 

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
