---
title: "03-Regression-Excerside13"
author: "Vasant Marur"
date: "5/15/2021"
output: 
  html_document:
    toc: true
    toc_depth: 4
    toc_float:
      collapsed: false
      smooth_scroll: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
set.seed(42)
suppressPackageStartupMessages(library(dplyr))
library(ISLR)
library(broom)
suppressPackageStartupMessages(library(ggplot2))


```

# Introduction
This is a write up of doing the Applied Exercise 13 of Chap. 3 of ISLR. 
Question 13 Description is below, each part of the question is in subsections below:

> In this exercise you will create some simulated data and will fit simple
> linear regression models to it. Make sure to use set.seed(1) prior to
> starting part (a) to ensure consistent results.

Note: We're setting seed to 42 as that is the answer to everything.

## Question 13 (a)
> (a) Using the rnorm() function, create a vector, x, containing 100
> observations drawn from a N(0, 1) distribution. This represents
> a feature, X.

```{r simulate100}
x <-rnorm(n = 100, mean = 0, sd = 1)
x %>% glimpse()
```

Let's also plot x You can also embed plots, for example:

```{r plotx, echo=FALSE}
plot(x)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
